Digital History in Finland, 1488-1828

### 2016-07-11 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@

>>>>

[Languages & religious texts in Finland]

### Development of use of different languages in Finnish National Bibliography

```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="160px", fig.show="hold"}
catalogue <- "Fennica"
df <- df0
langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
lang <- paste("language.", langs, sep = "")
otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
dfl <- NULL
for (lan in lang) {
  # Classify a document to the specifed language
  # If document is assigned with languages, each case is considered
  # so one doc may have multiple entries corresponding to different languages
  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
  # Combine data frames for specified languages
  dflsub <- filter(df, df[[lan]])
  if (nrow(dflsub) > 0) {
    dflsub$language <- gsub("language.", "", lan)
    dfl <- bind_rows(dfl, dflsub)
  }
}

# ----------------------------------

df <- dfl %>% filter(catalog == catalogue)
df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = n(),
                 paper = sum(paper.consumption.km2, na.rm = TRUE))

# PAPER CONSUMPTION
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(col = language, shape = language), size = 5) +
       geom_line(aes(col = language, shape = language)) +       
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
print(p)
```
---

@@

---
# Context

- Finnish knowledge production 1640-1828 can only be understood in the Swedish context.

- Academy of Turku as part of the Swedish University system is the centre of Finnish knowledge production.

### Challenges: nationally delineated perspectives by using nationally collected materials
